---
params:
  title: "Data Presentation"
  obj_path: "PATH"
  results_path: "PATH"
  final_cluster_param: "seurat_clusters"
title: <h9 >`r params$title`</h9>
author: <h7 >NAME</h7>   
date: <h7 >`r format(Sys.time(), '%d/%m/%Y')`</h7>
output:
  html_document:
    highlight: kate
    toc: yes
    toc_float: yes
    toc_depth: 6
    code_folding: hide
    theme: cosmo
    df_print: paged
    code_download: TRUE
editor_options: 
  chunk_output_type: inline
---

```{css, echo=FALSE}
h9 {
  font-size: 40px;
}

h1 { /* Header 1 */
  font-size: 34px;
}
h2 { /* Header 2 */
    font-size: 30px;
}
h3 { /* Header 3 */
  font-size: 28px;
}
h4 { /* Header 4 */
  font-size: 26px;
}
h5 { /* Header 5 */
  font-size: 24px;
}
h6 { /* Header 6 */
  font-size: 22px;
}
h7 { /* Header 6 */
  font-size: 20px;
  font-style: italic;
}
```




```{r Load Environment, include=FALSE}
## Load Environment
suppressPackageStartupMessages(library(Seurat))
suppressPackageStartupMessages(library(SeuratPipe))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tibble))
suppressPackageStartupMessages(library(patchwork))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(kableExtra))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(CIPR))
suppressPackageStartupMessages(library(ggbrace))
source("~/project/Functions/Utils.R")
seed <- 42 # Seed number for scipt
set.seed(seed) 

vector <- 1:1000 
subchonkify <- function(g, fig_width=5, fig_height=7, chunk_name = NULL, loop_variable = NULL, random_id = NULL) {
  name <- paste0(chunk_name,"_",loop_variable,"_",random_id)
  g_deparsed <- paste0(deparse(
    function() {g}
  ), collapse = '')

  sub_chunk <- paste0("```{r sub_chunk_", name, ", fig.height=",
   fig_height, ", fig.width=", fig_width, ", echo=FALSE, warning=FALSE, message=FALSE}",
  "\n(", 
    g_deparsed
    , ")()",
  "\n","```")

  cat(knitr::knit(text = knitr::knit_expand(text = sub_chunk), quiet = TRUE))
}
```


```{r Parameters, include=FALSE}
obj <- readRDS(params$obj_path)
seurat <- obj$seu
opts <- obj$opts

if(!is.null(opts$pcs_to_remove)) {
  marker_path <- paste0(params$results_path, "/seu_harmony_npcs", opts$npcs,"_r",paste0(opts$pcs_to_remove, collapse = ""), "/dim", opts$ndims,"/clusters/seu_markers_res", opts$res, ".csv")
} else {
  marker_path <- paste0(params$results_path, "/seu_harmony_npcs", opts$npcs, "/dim", opts$ndims,"/clusters/seu_markers_res", opts$res, ".csv")
}


markers <- read.csv(marker_path, row.names = 1)


seurat$seurat_clusters <- as.factor(seurat$seurat_clusters)
Idents(seurat) <- seurat$seurat_clusters
cell_type_markers <- flatten(opts$modules_group)
metadata <- opts$meta_to_plot
metadata <- c(metadata,"HCA_General_sctype","HCA_Specific_sctype","Hendo_sctype", "malat1_threshold")
```



# Workflow Options

```{r Workflow Options, echo=FALSE}
df <- as.data.frame(opts[c("npcs","ndims","res","n_hvgs","min.pct","logfc.threshold","topn_genes","diff_cluster_pct","pval_adj")])
kable(t(df)) %>%
  kable_styling(full_width = F,position = "left")
```


# Clusters - Numbered


```{r Cluster Numbers, fig.height=7, fig.width=7, fig.retina=3, results='asis', echo=FALSE}
dim_plot(seurat, group.by = "seurat_clusters", label = T, col_pal = opts$discrete_col_pal, raster = FALSE) 
```


# MetaData Plots 


## Meta Data Feature Plots {.tabset .tabset-pills}


```{r MetaData Plots, results='asis', echo=FALSE}
for (m in metadata){
  cat("\n")
  cat("###",m,"{.tabset}","\n")

  eval(parse(text=paste0("i <- nlevels(factor(seurat@meta.data$",m,"))"))) # Generate number of levels in each metadata to change plot size and layout
  if (i== 1){ # These pieces of metadata do not need a split version of the umap due to there only being one level
    p <- dim_plot(seurat, group.by=m, raster = FALSE)
    subchonkify(p, fig_width=8, fig_height=7, chunk_name = "MetaData_Plots", loop_variable = m, random_id = 1)
  } else if (i ==2) { # Split umaps are produced alongside normal umaps for those with 2 levels but the plot dimensions are set for better plotting visulalistion
    cat("\n")
    cat("####","Normal","\n")
    p <- dim_plot(seurat, group.by=m, col_pal = opts$discrete_col_pal, raster = FALSE)
    subchonkify(p, fig_width=8, fig_height=7, chunk_name = "MetaData_Plots", loop_variable = m, random_id = 2)
    cat("\n")
    cat("\n")
    cat("####","Split","\n")
    p <- dim_plot(seurat, group.by=m, split.by=m, ncol=2, col_pal = opts$discrete_col_pal, raster = FALSE) + NoLegend()
    subchonkify(p, fig_width=10, fig_height=6, chunk_name = "MetaData_Plots", loop_variable = m, random_id = 3)
    cat("\n")
  } else{ # Split umaps are produced alongside normal umaps for those with multiple levels
    cat("\n")
    cat("####","Normal","\n")
    p <- dim_plot(seurat, group.by=m, col_pal = opts$discrete_col_pal, raster = FALSE)
    subchonkify(p, fig_width=6+(ceiling(i/16)*2), fig_height=7, chunk_name = "MetaData_Plots", loop_variable = m, random_id = 4)
    cat("\n")
    cat("\n")
    cat("####","Split","\n")
    p <- dim_plot(seurat, group.by=m, split.by=m, ncol=3, col_pal = opts$discrete_col_pal, raster = FALSE) + NoLegend()
    subchonkify(p, fig_width=15, fig_height=5*(ceiling(i/3)), chunk_name = "MetaData_Plots", loop_variable = m, random_id = 5)
    cat("\n")
  }
  
  cat("\n")

}
```


## QC Plots {.tabset}


### Feature Plots

```{r QC Feature Plots - Feature Plots, results='asis', echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.height=9}
DefaultAssay(seurat) <- "RNA" 
p <- feature_plot(seurat, features = c("nCount_RNA","nFeature_RNA", "percent.mt","MALAT1"), ncol = 2, raster = FALSE) 
p
```

### Vln Plots

```{r QC Violin Plots - Vln Plots, results='asis', echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.height=10}
DefaultAssay(seurat) <- "RNA" 
p <- VlnPlot(seurat, features = c("nCount_RNA","nFeature_RNA", "percent.mt","MALAT1"), ncol = 2, pt.size = 0, cols = opts$discrete_col_pal) & geom_jitter(height = 0, size = 0.5, show.legend = FALSE, alpha=0.1)
p
```


### Correlation

```{r QC Correlations,results='asis', echo=FALSE, warning=FALSE, message=FALSE, fig.width=15, fig.height=10}
DefaultAssay(seurat) <- "RNA" 
pca_feature_cor_plot(seurat, features = c("nCount_RNA","nFeature_RNA", "percent.mt","MALAT1"))
```

### Batch Stats

```{r QC Batch Stats, echo=FALSE}
df1 <- seurat@meta.data %>%
  group_by(orig.ident) %>%
  summarise_at(vars(nFeature_RNA), list(name = median)) 
df1 <- as.data.frame(df1)
rownames(df1) <- df1$orig.ident


df2 <- seurat@meta.data %>%
  group_by(orig.ident) %>%
  summarise_at(vars(nCount_RNA), list(name = median))
df2 <- as.data.frame(df2)
rownames(df2) <- df2$orig.ident


df3 <- as.data.frame(table(seurat$orig.ident))
rownames(df3) <- df3$Var1

order <- sort(df1$orig.ident)
df1 <- df1[order,]
df2 <- df2[order,]
df3 <- df3[order,]

df <- cbind(df1,df2[,2],df3[,2])
rownames(df) <- NULL
colnames(df) <- c("Batch", "Median Features", "Median Counts", "Cell Number")

df <- df %>% mutate_if(is.numeric, ~round(., 0))

df %>%
  kbl() %>%
  kable_styling()
```


## Cluster Contribution Plots {.tabset}



### SAMPLE {.tabset .tabset-pills}

#### Cluster Percentage

```{r SAMPLE Cluster contribution, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
col_pal_many <- Polychrome::createPalette(nlevels(as.factor(seurat$SAMPLE)), opts$discrete_col_pal)
names(col_pal_many) <- NULL
subchonkify(percent_contribution_hist(metadata = seurat@meta.data, value = "SAMPLE", clusters = "seurat_clusters", col_pal = col_pal_many) + NoLegend(), fig_width = 7 + 0.3*nlevels(seurat@meta.data[["seurat_clusters"]]), chunk_name = "Orig.ident_Cluster_contribution", random_id = 1)
```

#### Relative Contribution

```{r SAMPLE Relative contribution, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
subchonkify(relative_contribution_hist(metadata = seurat@meta.data, value = "SAMPLE", clusters = "seurat_clusters", col_pal = col_pal_many) + NoLegend(), fig_height = 5, fig_width = 7 + 0.5*nlevels(seurat@meta.data[["seurat_clusters"]]), chunk_name = "Orig.ident_Relative_contribution", random_id = 1)
```

#### Table

```{r SAMPLE table, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
table(seurat$SAMPLE, seurat$seurat_clusters) %>%
  kbl() %>%
  kable_styling()%>% 
 scroll_box(width = "1000px")
```


### STUDY {.tabset .tabset-pills}


#### Cluster Percentage

```{r STUDY Cluster contribution, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
subchonkify(percent_contribution_hist(metadata = seurat@meta.data, value = "STUDY", clusters = "seurat_clusters", col_pal = opts$discrete_col_pal), fig_width = 7 + 0.3*nlevels(seurat@meta.data[["seurat_clusters"]]), chunk_name = "Condition_Cluster_contribution", random_id = 1)
```

#### Relative Contribution

```{r STUDY Relative contribution, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
subchonkify(relative_contribution_hist(metadata = seurat@meta.data, value = "STUDY", clusters = "seurat_clusters", col_pal = opts$discrete_col_pal), fig_height = 5, fig_width = 7 + 0.5*nlevels(seurat@meta.data[["seurat_clusters"]]), chunk_name = "Condition_Relative_contribution", random_id = 1)
```

#### Table

```{r STUDY table, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
table(seurat$STUDY, seurat$seurat_clusters) %>%
  kbl() %>%
  kable_styling()%>% 
 scroll_box(width = "1000px")
```




# Cell Type Markers {.tabset .tabset-pills}


```{r Cell Type Markers Plots, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
DefaultAssay(seurat) <- "RNA" 
for (j in 1:length(opts$modules_group)){
  cell_type_markers <- opts$modules_group[[j]]
  cat("\n")
  cat("##",names(opts$modules_group)[j],"{.tabset .tabset-pills}","\n")
  cat("\n")

  for (i in 1:length(cell_type_markers)) {
    name <- names(cell_type_markers[i])
    test <- sum(!cell_type_markers[[i]] %in% rownames(seurat))
    if (test > 0){
      cell_type_markers[[i]] <- cell_type_markers[[i]][cell_type_markers[[i]] %in% rownames(seurat)]
    }
  }
  
  all_names <- names(cell_type_markers)# Get name for file
  
  for (m in 1:length(cell_type_markers)){ # Cycle through gene geneset in the marker list from above
    genes <- cell_type_markers[[m]] # Get genes to plot

    name <- all_names[m]
  
    if (length(genes) > 0){ # Prevent Running this element if there are no genes after gene check
      ## set parameters for options in plotting
      if (length(genes) == 2){ 
        wid <- 10
        hei_feature <- 6
        ncols_feature <- 2
        hei_vln <- 6
        ncols_vln <- 2
        hei_dot <- 6
      } else {
        wid <- 15
        hei_feature <- 5*(ceiling((length(genes)/3)))
        ncols_feature <- 3
        hei_vln <- 5*(ceiling((length(genes)/2)))
        ncols_vln <- 2
        hei_dot <- length(genes)
      }
      if (hei_feature > 120){
        hei_feature <- 120
      }
      if (hei_vln > 120){
        hei_vln <- 120
      }
      cat("\n")
      cat("###",name,"{.tabset}","\n")
      
      ## Plot Featureplot with viridis colour scale, cells are ordered by value
      cat("\n")
      cat("####","Feature","\n")
      p <- feature_plot(seurat, features = genes, ncol = ncols_feature, order = T, raster = FALSE) 
      subchonkify(p, fig_width=wid, fig_height=hei_feature, chunk_name = "Cell_Type_Markers_Plots", loop_variable = paste0(names(opts$modules_group)[j],"_",name), random_id = 1)
      cat("\n")
      
      ### Plot VlnPlot with respective clustering    
      cat("\n")
      cat("####","Violin","\n")
      p <- VlnPlot(seurat, features = genes, ncol = ncols_vln, pt.size = 0, cols = opts$discrete_col_pal) & geom_jitter(height = 0, size = 0.5, show.legend = FALSE, alpha=0.1)
      subchonkify(p, fig_width=wid, fig_height=hei_vln, chunk_name = "Cell_Type_Markers_Plots", loop_variable = paste0(names(opts$modules_group)[j],"_",name), random_id = 2)
      cat("\n")
      
      
      ### Plot DotPlot with respective clustering    
      cat("\n")
      cat("####","Dot Plot","\n")
      p <- dot_plot_gene(seurat, features = genes, scale.min = 0, scale.max = 100)
      subchonkify(p, fig_width=wid, fig_height=hei_dot, chunk_name = "Cell_Type_Markers_Plots", loop_variable = paste0(names(opts$modules_group)[j],"_",name), random_id = 3)
      cat("\n")
      
    }
  }
}
```



# Signautres {.tabset}


```{r Signatures, echo=FALSE}
cell_type_markers <- flatten(opts$modules_group)
sig <- gsub("^.*?\\.", "", names(cell_type_markers))
```

## Feature

```{r Signatures - Feature, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
if (length(sig) > 0){
  p <- feature_plot(seurat, features = sig, ncol = 3, order = T, raster = FALSE) 
  subchonkify(p, fig_width=15, fig_height=105, chunk_name = "Signatures_Feature", random_id = 1)# Needed to manually set fig height as plot wasnt being put into html. Assume its to do with DPI of plot but not had this issue with other so its not fully clear. The manual setting solved the issue.
}
```

## Violin

```{r Signatures - Violin, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
if (length(sig) > 0){
  hei_vln <- 5*(ceiling((length(sig)/2)))
  if (hei_vln > 120){
    hei_vln <- 120
  }
  p <- VlnPlot(seurat, features = sig, ncol = 2, pt.size = 0, cols = opts$discrete_col_pal) & geom_jitter(height = 0, size = 0.5, show.legend = FALSE, alpha=0.1)
  subchonkify(p, fig_width=15, fig_height= hei_vln, chunk_name = "Signatures_Violin", random_id = 1)
}
```

## DotPlot

```{r Signautre - DotPlot, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
if (length(sig) > 0){
  p <- dot_plot(seurat, features = sig, scale.min = 0, scale.max = 100)
  subchonkify(p, fig_width=20, fig_height=15, chunk_name = "Signatures_dotplot", random_id = 1)
}
```




# Henderson Gene Amalgamated Dotplot

```{r Henderson Amalgamated Dotplot,message=FALSE, warning=FALSE, echo=FALSE,fig.width= 15, fig.height= 15} 
tmp <- seurat
tmp$seurat_clusters <- factor(seurat$seurat_clusters, levels = c(0,1,2,3,4,5,6,7,8,9,10,11,12,15,16,18,19,21,22,23,24,25,27,28,29,30,31,32,   13,14,17,20,26,33,34,35,36,37,38,39,40,41,42))
Idents(tmp) <- "Alpha.Annotations.tmp"

plot <- DotPlot(tmp, features = unique(c(unlist(opts$modules_group$Hendo), "NRXN1","ERBB3","SOX10","S100B")), group.by = "seurat_clusters") + ggplot2::coord_flip(x=c(1,73), y=c(1,43),clip = "off") + 
  eval(rlang::expr(ggplot2::scale_colour_distiller(name = NULL,type = "div", palette = "RdYlBu"))) + 
  theme(axis.title.x = element_text(margin = margin(t = 80))) + theme(axis.title.y = element_text(margin = margin(r = 130))) +
  ggplot2::theme(legend.position = "right") + 
  geom_brace(xstart = -1, xend = -3, ystart = 1, yend = 28,pointing="side") +
  annotate("text",x=-5,y=14,label="Hepatocyte",angle = 45) +
  geom_brace(xstart = -1, xend = -3, ystart = 29, yend = 43,pointing="side") +
  annotate("text",x=-4.5,y=36,label="Doublet",angle = 45) +

  geom_brace(xstart = 1, xend = 7, ystart = -3.5, yend = -4.5) +
  annotate("text",x=3,y=-6,label="Hepatocytes",angle = 45) +
  geom_brace(xstart = 8, xend = 14, ystart = -3.5, yend = -4.5) +
  annotate("text",x=10.5,y=-6,label="Cholangiocytes",angle = 45) +
  geom_brace(xstart = 15, xend = 22, ystart = -3.5, yend = -4.5) +
  annotate("text",x=17.5,y=-6,label="Endothelia",angle = 45) +
  geom_brace(xstart = 23, xend = 31, ystart = -3.5, yend = -4.5) +
  annotate("text",x=26,y=-6,label="Mesenchyme",angle = 45) +
  geom_brace(xstart = 32, xend = 33, ystart = -3.5, yend = -4.5) +
  annotate("text",x=31.5,y=-6,label="Mesothelia",angle = 45) +
  geom_brace(xstart = 34, xend = 37, ystart = -3.5, yend = -4.5) +
  annotate("text",x=34.5,y=-6,label="Leucocytes",angle = 45) +
  geom_brace(xstart = 38, xend = 43, ystart = -3.5, yend = -4.5) +
  annotate("text",x=40.5,y=-6,label="MPs",angle = 45) +
  geom_brace(xstart = 44, xend = 46, ystart = -3.5, yend = -4.5) +
  annotate("text",x=44,y=-6,label="Lymphocytes",angle = 45) +
  geom_brace(xstart = 47, xend = 52, ystart = -3.5, yend = -4.5) +
  annotate("text",x=49,y=-5.8,label="T Cells",angle = 45) +
  geom_brace(xstart = 53, xend = 54, ystart = -3.5, yend = -4.5) +
  annotate("text",x=53,y=-5.8,label="B Cells",angle = 45) +
  geom_brace(xstart = 55, xend = 56, ystart = -3.5, yend = -4.5) +
  annotate("text",x=55.5,y=-5,label="ILCs",angle = 45) +
  geom_brace(xstart = 57, xend = 58, ystart = -3.5, yend = -4.5) +
  annotate("text",x=57,y=-5.9,label="Mast Cells",angle = 45) +
  geom_brace(xstart = 59, xend = 60, ystart = -3.5, yend = -4.5) +
  annotate("text",x=59.5,y=-5.5,label="PDCs",angle = 45) +
  geom_brace(xstart = 61, xend = 64, ystart = -3.5, yend = -4.5) +
  annotate("text",x=61.5,y=-5.9,label="Erythrocytes",angle = 45) +
  geom_brace(xstart = 65, xend = 65, ystart = -3.5, yend = -4.5) +
  annotate("text",x=64,y=-5.9,label="Neutrophils",angle = 45) +
  geom_brace(xstart = 66, xend = 69, ystart = -3.5, yend = -4.5) +
  annotate("text",x=67,y=-5.8,label="Cycling",angle = 45) +
  geom_brace(xstart = 70, xend = 73, ystart = -3.5, yend = -4.5) +
  annotate("text",x=71.5,y=-5.8,label="Neuronal",angle = 45) +
  
  theme(plot.margin = unit(c(0.01, 0.01, 0.05, 0.05), units="npc"))

plot



```




# Clusters Notes

```{r Cluster Names - Text, echo=FALSE, results="asis"}
if (file.exists(paste0(params$results_path,"/cluster_text.txt"))){
  cat(readLines(paste0(params$results_path,"/cluster_text.txt")), sep = '\n')
} else {
  file.create(paste0(params$results_path,"/cluster_text.txt"))
  cat(readLines(paste0(params$results_path,"/cluster_text.txt")), sep = '\n')
}
```

# Clusters - Names {.tabset}

```{r Cluster Names - Plots, fig.height=7, fig.width=7, fig.retina=3, results='asis', echo=FALSE}
for (i in params$final_cluster_param){
        cat("\n")
        cat("##",i,"\n")
        p <- dim_plot(seurat, group.by = i, label = F, col_pal = opts$discrete_col_pal, raster = FALSE)
        subchonkify(p, fig_width=10, fig_height=7, chunk_name = "Cluster_name", loop_variable = i, random_id = 1)
        cat("\n")
}

```


#


## Session Info

```{r Session Info}
sessionInfo()
```


