---
params:
  title: "Data Presentation"
  obj_path: "PATH"
  results_path: "PATH"
  final_cluster_param: "seurat_clusters"
title: <h9 >`r params$title`</h9>
author: <h7 >NAME</h7>   
date: <h7 >`r format(Sys.time(), '%d/%m/%Y')`</h7>
output:
  html_document:
    highlight: kate
    toc: yes
    toc_float: yes
    toc_depth: 6
    code_folding: hide
    theme: cosmo
    df_print: paged
    code_download: TRUE
editor_options: 
  chunk_output_type: inline
---

```{css, echo=FALSE}
h9 {
  font-size: 40px;
}

h1 { /* Header 1 */
  font-size: 34px;
}
h2 { /* Header 2 */
    font-size: 30px;
}
h3 { /* Header 3 */
  font-size: 28px;
}
h4 { /* Header 4 */
  font-size: 26px;
}
h5 { /* Header 5 */
  font-size: 24px;
}
h6 { /* Header 6 */
  font-size: 22px;
}
h7 { /* Header 6 */
  font-size: 20px;
  font-style: italic;
}
```




```{r Load Environment, include=FALSE}
## Load Environment
suppressPackageStartupMessages(library(Seurat))
suppressPackageStartupMessages(library(SeuratPipe))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(tibble))
suppressPackageStartupMessages(library(patchwork))
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(kableExtra))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(CIPR))
source("~/project/Functions/Utils.R")
seed <- 42 # Seed number for scipt
set.seed(seed) 

vector <- 1:1000 
subchonkify <- function(g, fig_width=5, fig_height=7, chunk_name = NULL, loop_variable = NULL, random_id = NULL) {
  name <- paste0(chunk_name,"_",loop_variable,"_",random_id)
  g_deparsed <- paste0(deparse(
    function() {g}
  ), collapse = '')

  sub_chunk <- paste0("```{r sub_chunk_", name, ", fig.height=",
   fig_height, ", fig.width=", fig_width, ", echo=FALSE, warning=FALSE, message=FALSE}",
  "\n(", 
    g_deparsed
    , ")()",
  "\n","```")

  cat(knitr::knit(text = knitr::knit_expand(text = sub_chunk), quiet = TRUE))
}
```


```{r Parameters, include=FALSE}
obj <- readRDS(params$obj_path)
seurat <- obj$seu
opts <- obj$opts

if(!is.null(opts$pcs_to_remove)) {
  marker_path <- paste0(params$results_path, "/seu_harmony_npcs", opts$npcs,"_r",paste0(opts$pcs_to_remove, collapse = ""), "/dim", opts$ndims,"/clusters/seu_markers_res", opts$res, ".csv")
} else {
  marker_path <- paste0(params$results_path, "/seu_harmony_npcs", opts$npcs, "/dim", opts$ndims,"/clusters/seu_markers_res", opts$res, ".csv")
}


markers <- read.csv(marker_path, row.names = 1)


seurat$seurat_clusters <- as.factor(seurat$seurat_clusters)
Idents(seurat) <- seurat$seurat_clusters
cell_type_markers <- flatten(opts$modules_group)
metadata <- opts$meta_to_plot
metadata <- c(metadata,"HCA_General_sctype","HCA_Specific_sctype","Hendo_sctype", "malat1_threshold")
```



# Workflow Options

```{r Workflow Options, echo=FALSE}
df <- as.data.frame(opts[c("npcs","ndims","res","n_hvgs","min.pct","logfc.threshold","topn_genes","diff_cluster_pct","pval_adj")])
kable(t(df)) %>%
  kable_styling(full_width = F,position = "left")
```


# Clusters - Numbered


```{r Cluster Numbers, fig.height=7, fig.width=7, fig.retina=3, results='asis', echo=FALSE}
dim_plot(seurat, group.by = "seurat_clusters", label = T, col_pal = opts$discrete_col_pal, raster = FALSE) 
```


# MetaData Plots 


## Meta Data Feature Plots {.tabset .tabset-pills}


```{r MetaData Plots, results='asis', echo=FALSE}
for (m in metadata){
  cat("\n")
  cat("###",m,"{.tabset}","\n")

  eval(parse(text=paste0("i <- nlevels(factor(seurat@meta.data$",m,"))"))) # Generate number of levels in each metadata to change plot size and layout
  if (i== 1){ # These pieces of metadata do not need a split version of the umap due to there only being one level
    p <- dim_plot(seurat, group.by=m, raster = FALSE)
    subchonkify(p, fig_width=8, fig_height=7, chunk_name = "MetaData_Plots", loop_variable = m, random_id = 1)
  } else if (i ==2) { # Split umaps are produced alongside normal umaps for those with 2 levels but the plot dimensions are set for better plotting visulalistion
    cat("\n")
    cat("####","Normal","\n")
    p <- dim_plot(seurat, group.by=m, col_pal = opts$discrete_col_pal, raster = FALSE)
    subchonkify(p, fig_width=8, fig_height=7, chunk_name = "MetaData_Plots", loop_variable = m, random_id = 2)
    cat("\n")
    cat("\n")
    cat("####","Split","\n")
    p <- dim_plot(seurat, group.by=m, split.by=m, ncol=2, col_pal = opts$discrete_col_pal, raster = FALSE) + NoLegend()
    subchonkify(p, fig_width=10, fig_height=6, chunk_name = "MetaData_Plots", loop_variable = m, random_id = 3)
    cat("\n")
  } else{ # Split umaps are produced alongside normal umaps for those with multiple levels
    cat("\n")
    cat("####","Normal","\n")
    p <- dim_plot(seurat, group.by=m, col_pal = opts$discrete_col_pal, raster = FALSE)
    subchonkify(p, fig_width=6+(ceiling(i/16)*2), fig_height=7, chunk_name = "MetaData_Plots", loop_variable = m, random_id = 4)
    cat("\n")
    cat("\n")
    cat("####","Split","\n")
    p <- dim_plot(seurat, group.by=m, split.by=m, ncol=3, col_pal = opts$discrete_col_pal, raster = FALSE) + NoLegend()
    subchonkify(p, fig_width=15, fig_height=5*(ceiling(i/3)), chunk_name = "MetaData_Plots", loop_variable = m, random_id = 5)
    cat("\n")
  }
  
  cat("\n")

}
```


## QC Plots {.tabset}


### Feature Plots

```{r QC Feature Plots - Feature Plots, results='asis', echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.height=9}
DefaultAssay(seurat) <- "RNA" 
p <- feature_plot(seurat, features = c("nCount_RNA","nFeature_RNA", "percent.mt","MALAT1"), ncol = 2, raster = FALSE) 
p
```

### Vln Plots

```{r QC Violin Plots - Vln Plots, results='asis', echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.height=10}
DefaultAssay(seurat) <- "RNA" 
p <- VlnPlot(seurat, features = c("nCount_RNA","nFeature_RNA", "percent.mt","MALAT1"), ncol = 2, pt.size = 0, cols = opts$discrete_col_pal) & geom_jitter(height = 0, size = 0.5, show.legend = FALSE, alpha=0.1)
p
```


### Correlation

```{r QC Correlations,results='asis', echo=FALSE, warning=FALSE, message=FALSE, fig.width=15, fig.height=10}
DefaultAssay(seurat) <- "RNA" 
pca_feature_cor_plot(seurat, features = c("nCount_RNA","nFeature_RNA", "percent.mt","MALAT1"))
```

### Batch Stats

```{r QC Batch Stats, echo=FALSE}
df1 <- seurat@meta.data %>%
  group_by(orig.ident) %>%
  summarise_at(vars(nFeature_RNA), list(name = median)) 
df1 <- as.data.frame(df1)
rownames(df1) <- df1$orig.ident


df2 <- seurat@meta.data %>%
  group_by(orig.ident) %>%
  summarise_at(vars(nCount_RNA), list(name = median))
df2 <- as.data.frame(df2)
rownames(df2) <- df2$orig.ident


df3 <- as.data.frame(table(seurat$orig.ident))
rownames(df3) <- df3$Var1

order <- sort(df1$orig.ident)
df1 <- df1[order,]
df2 <- df2[order,]
df3 <- df3[order,]

df <- cbind(df1,df2[,2],df3[,2])
rownames(df) <- NULL
colnames(df) <- c("Batch", "Median Features", "Median Counts", "Cell Number")

df <- df %>% mutate_if(is.numeric, ~round(., 0))

df %>%
  kbl() %>%
  kable_styling()
```



## Cluster Contribution Plots {.tabset}



### SAMPLE {.tabset .tabset-pills}

#### Cluster Percentage

```{r SAMPLE Cluster contribution, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
col_pal_many <- Polychrome::createPalette(nlevels(as.factor(seurat$SAMPLE)), opts$discrete_col_pal)
names(col_pal_many) <- NULL
subchonkify(percent_contribution_hist(metadata = seurat@meta.data, value = "SAMPLE", clusters = "seurat_clusters", col_pal = col_pal_many) + NoLegend(), fig_width = 7 + 0.3*nlevels(seurat@meta.data[["seurat_clusters"]]), chunk_name = "Orig.ident_Cluster_contribution", random_id = 1)
```

#### Relative Contribution

```{r SAMPLE Relative contribution, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
subchonkify(relative_contribution_hist(metadata = seurat@meta.data, value = "SAMPLE", clusters = "seurat_clusters", col_pal = col_pal_many) + NoLegend(), fig_height = 5, fig_width = 7 + 0.5*nlevels(seurat@meta.data[["seurat_clusters"]]), chunk_name = "Orig.ident_Relative_contribution", random_id = 1)
```

#### Table

```{r SAMPLE table, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
table(seurat$SAMPLE, seurat$seurat_clusters) %>%
  kbl() %>%
  kable_styling()
```


### STUDY {.tabset .tabset-pills}


#### Cluster Percentage

```{r STUDY Cluster contribution, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
subchonkify(percent_contribution_hist(metadata = seurat@meta.data, value = "STUDY", clusters = "seurat_clusters", col_pal = opts$discrete_col_pal), fig_width = 7 + 0.3*nlevels(seurat@meta.data[["seurat_clusters"]]), chunk_name = "Condition_Cluster_contribution", random_id = 1)
```

#### Relative Contribution

```{r STUDY Relative contribution, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
subchonkify(relative_contribution_hist(metadata = seurat@meta.data, value = "STUDY", clusters = "seurat_clusters", col_pal = opts$discrete_col_pal), fig_height = 5, fig_width = 7 + 0.5*nlevels(seurat@meta.data[["seurat_clusters"]]), chunk_name = "Condition_Relative_contribution", random_id = 1)
```

#### Table

```{r STUDY table, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
table(seurat$STUDY, seurat$seurat_clusters) %>%
  kbl() %>%
  kable_styling()
```




# Cell Type Markers {.tabset .tabset-pills}


```{r Cell Type Markers Plots, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
DefaultAssay(seurat) <- "RNA"
for (j in 1:length(opts$modules_group)){
  cell_type_markers <- opts$modules_group[[j]]
  cat("\n")
  cat("##",names(opts$modules_group)[j],"{.tabset .tabset-pills}","\n")
  cat("\n")

  for (i in 1:length(cell_type_markers)) {
    name <- names(cell_type_markers[i])
    test <- sum(!cell_type_markers[[i]] %in% rownames(seurat))
    if (test > 0){
      cell_type_markers[[i]] <- cell_type_markers[[i]][cell_type_markers[[i]] %in% rownames(seurat)]
    }
  }
  
  all_names <- names(cell_type_markers)# Get name for file
  
  for (m in 1:length(cell_type_markers)){ # Cycle through gene geneset in the marker list from above
    genes <- cell_type_markers[[m]] # Get genes to plot

    name <- all_names[m]
  
    if (length(genes) > 0){ # Prevent Running this element if there are no genes after gene check
      ## set parameters for options in plotting
      if (length(genes) == 2){ 
        wid <- 10
        hei_feature <- 6
        ncols_feature <- 2
        hei_vln <- 6
        ncols_vln <- 2
        hei_dot <- 6
      } else {
        wid <- 15
        hei_feature <- 5*(ceiling((length(genes)/3)))
        ncols_feature <- 3
        hei_vln <- 5*(ceiling((length(genes)/2)))
        ncols_vln <- 2
        hei_dot <- length(genes)
      }
      if (hei_feature > 120){
        hei_feature <- 120
      }
      if (hei_vln > 120){
        hei_vln <- 120
      }
      cat("\n")
      cat("###",name,"{.tabset}","\n")
      
      ## Plot Featureplot with viridis colour scale, cells are ordered by value
      cat("\n")
      cat("####","Feature","\n")
      p <- feature_plot(seurat, features = genes, ncol = ncols_feature, order = T, raster = FALSE) 
      subchonkify(p, fig_width=wid, fig_height=hei_feature, chunk_name = "Cell_Type_Markers_Plots", loop_variable = paste0(names(opts$modules_group)[j],"_",name), random_id = 1)
      cat("\n")
      
      ### Plot VlnPlot with respective clustering    
      cat("\n")
      cat("####","Violin","\n")
      p <- VlnPlot(seurat, features = genes, ncol = ncols_vln, pt.size = 0, cols = opts$discrete_col_pal) & geom_jitter(height = 0, size = 0.5, show.legend = FALSE, alpha=0.1)
      subchonkify(p, fig_width=wid, fig_height=hei_vln, chunk_name = "Cell_Type_Markers_Plots", loop_variable = paste0(names(opts$modules_group)[j],"_",name), random_id = 2)
      cat("\n")
      
      
      ### Plot DotPlot with respective clustering    
      cat("\n")
      cat("####","Dot Plot","\n")
      p <- dot_plot_gene(seurat, features = genes, scale.min = 0, scale.max = 100)
      subchonkify(p, fig_width=wid, fig_height=hei_dot, chunk_name = "Cell_Type_Markers_Plots", loop_variable = paste0(names(opts$modules_group)[j],"_",name), random_id = 3)
      cat("\n")
      
    }
  }
}
```



# Signautres {.tabset}


```{r Signatures, echo=FALSE}
cell_type_markers <- flatten(opts$modules_group)
sig <- gsub("^.*?\\.", "", names(cell_type_markers))
```

## Feature

```{r Signatures - Feature, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
if (length(sig) > 0){
  p <- feature_plot(seurat, features = sig, ncol = 3, order = T, raster = FALSE) 
  subchonkify(p, fig_width=15, fig_height=5*(ceiling((length(sig)/3))), chunk_name = "Signatures_Feature", random_id = 1)
}
```

## Violin

```{r Signatures - Violin, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
if (length(sig) > 0){
  hei_vln <- 5*(ceiling((length(sig)/2)))
  if (hei_vln > 120){
    hei_vln <- 120
  }
  p <- VlnPlot(seurat, features = sig, ncol = 2, pt.size = 0, cols = opts$discrete_col_pal) & geom_jitter(height = 0, size = 0.5, show.legend = FALSE, alpha=0.1)
  subchonkify(p, fig_width=15, fig_height= hei_vln, chunk_name = "Signatures_Violin", random_id = 1)
}
```

## DotPlot

```{r Signautre - DotPlot, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
if (length(sig) > 0){
  p <- dot_plot(seurat, features = sig, scale.min = 0, scale.max = 100)
  subchonkify(p, fig_width=20, fig_height=15, chunk_name = "Signatures_dotplot", random_id = 1)
}
```


# Markers


## Top 10 Markers {.tabset .tabset-pills}


```{r Choose top10 markers, include=FALSE}
top10 <- markers[markers$gene %in% rownames(x = seurat), ] |>
  dplyr::filter(p_val_adj < 0.05) |>
  dplyr::group_by(cluster) |>
  dplyr::filter(pct.1 - pct.2 > 0.1) |>
  dplyr::slice_max(n = 10, order_by = avg_log2FC)
top10$cluster <- as.factor(top10$cluster)
```



```{r Print Cluster Markers, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
for (l in levels(top10$cluster)){
  if (nrow(top10[top10$cluster==l,]) > 0) { # Only print genes if there are marker genes for that cluster
    genes <- top10$gene[top10$cluster == l] # get genes for the specific cluster
    
    cat("\n")
    cat("###","Cluster",l,"{.tabset}","\n")
    
    cat("\n")
    cat("####","Feature","\n")
    p <- feature_plot(seurat, features=genes, reduction="umap",ncol=3, raster = FALSE) 
    subchonkify(p, fig_width=15, fig_height=5*(ceiling((length(genes)/3))), chunk_name = "Print_Cluster_Markers", loop_variable = l, random_id = 1)
    cat("\n")
    
    
    cat("\n")
    cat("####","Violin","\n")
    p <- VlnPlot(seurat, features=genes,ncol=2, pt.size = 0, cols = opts$discrete_col_pal) & geom_jitter(height = 0, size = 0.5, show.legend = FALSE, alpha=0.1) # Print violin plots with no points.
    subchonkify(p, fig_width=15, fig_height=5*(ceiling((length(genes)/2))), chunk_name = "Print_Cluster_Markers", loop_variable = l, random_id = 2)
    cat("\n")
    
    
    cat("\n")
    cat("####","Split Violin STUDY","\n")
    p <- VlnPlot(seurat, features=genes,ncol=1, split.by = "STUDY", pt.size = 0, cols = opts$discrete_col_pal)
    subchonkify(p, fig_width=15, fig_height=5*(ceiling((length(genes)))), chunk_name = "Print_Cluster_Markers", loop_variable = l, random_id = 3)
    cat("\n")

    
    cat("\n")
    cat("####","Split Violin - Cluster","\n")
    p <- VlnPlot(seurat, features=genes,ncol=1, idents = l, split.by = "SAMPLE", group.by = "SAMPLE", pt.size = 0, cols = opts$discrete_col_pal)
    subchonkify(p, fig_width=15, fig_height=5*(ceiling((length(genes)))), chunk_name = "Print_Cluster_Markers", loop_variable = l, random_id = 4)
    cat("\n")
  
  }
}
```

# CIPR Results


```{r CIPR - Run, echo=FALSE, message=FALSE, warning=FALSE}
significant_markers <- markers[markers$gene %in% rownames(x = seurat), ] |>
  dplyr::filter(p_val_adj < 0.05) 

CIPR(input_dat = significant_markers,
     comp_method = "logfc_dot_product", 
     reference = "hpca", 
     plot_ind = F,
     plot_top = F, 
     global_results_obj = T, 
     global_plot_obj = T)
```
 
 
```{r CIPR - Print Dot plot, fig.height=10, fig.width=15, fig.retina=3, echo=FALSE,message=FALSE, warning=FALSE}
top_plots
```

```{r CIPR - Print table, echo=FALSE}
rmarkdown::paged_table(CIPR_top_results)
```


# Map Clusters to Whole Dataset  {.tabset}

## Plots

```{r Map Data Back, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
whole <- readRDS("~/project/Liver_Cell_Atlas/Analysis_02/01_Broad_Cell_Annotations/seu.rds")
plots <- list()
for (i in levels(seurat$seurat_clusters)){
  plot1 <- DimPlot(whole, cells.highlight = colnames(seurat)[seurat$seurat_clusters == i], raster = FALSE) & ggtitle(paste0("Cluster ",i))
  plots[[i]] <- plot1
}
subchonkify(wrap_plots(plots, ncol = 3), fig_width=15, fig_height=5*(ceiling((length(plots)/3))), chunk_name = "MapBack", loop_variable = 1, random_id = 1)
```

## Table

```{r Map Clusters table, echo=FALSE}
seurat_meta <- seurat@meta.data[,"seurat_clusters", drop=FALSE ]
colnames(seurat_meta) <- "Lineage_Clustering"
whole_meta <- whole@meta.data[rownames(seurat_meta),"seurat_clusters",drop=FALSE]
colnames(whole_meta) <- "Whole_Dataset_Clustering"

df <- cbind(seurat_meta, whole_meta)
df2 <- table(df$Whole_Dataset_Clustering, df$Lineage_Clustering)

df2 %>%
  kbl() %>%
  kable_styling()
```


# Map Clusters to Unclean Mesenchyme Dataset  {.tabset}

## Plots

```{r Map Data Back - Unclean Mes, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
unclean_obj <- readRDS("~/project/Liver_Cell_Atlas/Analysis_02/02_Lineages_itr01/01_Mesenchyme/01_PreClean/chosen_parameters/Mesenchyme_unclean.rds")
unclean <- unclean_obj$seu
plots <- list()
for (i in levels(seurat$seurat_clusters)){
  plot1 <- DimPlot(unclean, cells.highlight = colnames(seurat)[seurat$seurat_clusters == i], raster = FALSE) & ggtitle(paste0("Cluster ",i))
  plots[[i]] <- plot1
}
subchonkify(wrap_plots(plots, ncol = 3), fig_width=15, fig_height=5*(ceiling((length(plots)/3))), chunk_name = "MapBack_Mes", loop_variable = 1, random_id = 1)
```

## Table

```{r Map Clusters table - Unclean Mes, echo=FALSE}
seurat_meta <- seurat@meta.data[,"seurat_clusters", drop=FALSE ]
colnames(seurat_meta) <- "Lineage_Clustering"
unclean_meta <- unclean@meta.data[rownames(seurat_meta),"seurat_clusters",drop=FALSE]
colnames(unclean_meta) <- "Unclean_Dataset_Clustering"

df <- cbind(seurat_meta, unclean_meta)
df2 <- table(df$Unclean_Dataset_Clustering, df$Lineage_Clustering)

df2 %>%
  kbl() %>%
  kable_styling()
```


# Mesenchyme Sub Population Genes - Henderson List {.tabset}



```{r Mesenchyme Sub Pop Markers, results='asis', message=FALSE, warning=FALSE, echo=FALSE}
DefaultAssay(seurat) <- "RNA"
sub_pop <- list(Portal_Fibroblasts = c("LAMC3", "SPON1", "C7", "FBLN1"),
                HSCs = c("RELN", "HHIP", "COLEC10", "VIPR1"),
                VSMCs = c("RGS6", "RGS5", "MYH11"))


  
  all_names <- names(sub_pop)# Get name for file
  
  for (m in 1:length(sub_pop)){ # Cycle through gene geneset in the marker list from above
    genes <- sub_pop[[m]] # Get genes to plot

    name <- all_names[m]
  
    if (length(genes) > 0){ # Prevent Running this element if there are no genes after gene check
      ## set parameters for options in plotting
      if (length(genes) == 2){ 
        wid <- 10
        hei_feature <- 6
        ncols_feature <- 2
        hei_vln <- 6
        ncols_vln <- 2
        hei_dot <- 6
      } else {
        wid <- 15
        hei_feature <- 5*(ceiling((length(genes)/3)))
        ncols_feature <- 3
        hei_vln <- 5*(ceiling((length(genes)/2)))
        ncols_vln <- 2
        hei_dot <- length(genes)
      }
      if (hei_feature > 120){
        hei_feature <- 120
      }
      if (hei_vln > 120){
        hei_vln <- 120
      }
      cat("\n")
      cat("##",name,"{.tabset .tabset-pills}","\n")
      
      ## Plot Featureplot with viridis colour scale, cells are ordered by value
      cat("\n")
      cat("###","Feature","\n")
      p <- feature_plot(seurat, features = genes, ncol = ncols_feature, order = T, raster = FALSE) 
      subchonkify(p, fig_width=wid, fig_height=hei_feature, chunk_name = "Sub_Pop_Markers_Plots", loop_variable = name, random_id = 1)
      cat("\n")
      
      ### Plot VlnPlot with respective clustering    
      cat("\n")
      cat("###","Violin","\n")
      p <- VlnPlot(seurat, features = genes, ncol = ncols_vln, pt.size = 0, cols = opts$discrete_col_pal) & geom_jitter(height = 0, size = 0.5, show.legend = FALSE, alpha=0.1)
      subchonkify(p, fig_width=wid, fig_height=hei_vln, chunk_name = "Sub_Pop_Markers_Plots", loop_variable = name, random_id = 2)
      cat("\n")
      
      
      ### Plot DotPlot with respective clustering    
      cat("\n")
      cat("###","Dot Plot","\n")
      p <- dot_plot_gene(seurat, features = genes, scale.min = 0, scale.max = 100)
      subchonkify(p, fig_width=wid, fig_height=hei_dot, chunk_name = "Sub_Pop_Markers_Plots", loop_variable = name, random_id = 3)
      cat("\n")
      
    }
  }

```


# Rachel Neuronal / Glial Genes {.tabset}

These Genes were kindly provided by Rachel. They were marker genes she identified for a neuronal/Glial cell populations in her data. They indeed also highlight the same neuronal cluster in this data and therefore would suggested that Neuronal/Glial cells is an appropriate name for these cells. However, this can be discussed.

## Feature Plot

```{r, results='asis', message=FALSE, warning=FALSE, echo=FALSE, fig.width=15, fig.height=10}
feature_plot(seurat, features = c("NRXN1","ERBB3","SOX10","S100B"), ncol = 3, order = T, raster = FALSE) 
```

## Violin Plot


```{r, results='asis', message=FALSE, warning=FALSE, echo=FALSE, fig.width=15, fig.height=10}
VlnPlot(seurat, features = c("NRXN1","ERBB3","SOX10","S100B"), ncol = 2, pt.size = 0, cols = opts$discrete_col_pal) & geom_jitter(height = 0, size = 0.5, show.legend = FALSE, alpha=0.1)
```

## Dot Plot

```{r, results='asis', message=FALSE, warning=FALSE, echo=FALSE, fig.width=15, fig.height=5}
dot_plot_gene(seurat, features = c("NRXN1","ERBB3","SOX10","S100B"), scale.min = 0, scale.max = 100)
```


# Clusters Notes

```{r Cluster Names - Text, echo=FALSE, results="asis"}
if (file.exists(paste0(params$results_path,"/cluster_text.txt"))){
  cat(readLines(paste0(params$results_path,"/cluster_text.txt")), sep = '\n')
} else {
  file.create(paste0(params$results_path,"/cluster_text.txt"))
  cat(readLines(paste0(params$results_path,"/cluster_text.txt")), sep = '\n')
}
```

# Clusters - Names {.tabset}

```{r Cluster Names - Plots, fig.height=7, fig.width=7, fig.retina=3, results='asis', echo=FALSE}
for (i in params$final_cluster_param){
        cat("\n")
        cat("##",i,"\n")
        p <- dim_plot(seurat, group.by = i, label = F, col_pal = opts$discrete_col_pal, raster = FALSE)
        subchonkify(p, fig_width=10, fig_height=7, chunk_name = "Cluster_name", loop_variable = i, random_id = 1)
        cat("\n")
}

```


# Notes

```{r Notes, echo=FALSE, results="asis"}
if (file.exists(paste0(params$results_path,"/notes_text.txt"))){
  cat(readLines(paste0(params$results_path,"/notes_text.txt")), sep = '\n')
} else {
  file.create(paste0(params$results_path,"/notes_text.txt"))
  cat(readLines(paste0(params$results_path,"/notes_text.txt")), sep = '\n')
}
```


## Session Info

```{r Session Info}
sessionInfo()
```


